The Astropy Project:

### 2017-09-23 main.tex
Update on Overleaf.
draft of introduction

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major astropy principles not mentioned in the first paper, the core v2.0 package, and infrastructure in astropy project to support development in python.
	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
    \item If your subpackage was included in Paper I, then please just include a note on what the package does, a reference to paper I, and any new major updates to your package
    \item If your subpackage was not included, then please a further description of the sub-package on level with what was in the first paper, and highlight any major features in it.   Typically length should be equivalent to one column
    \item Please make sure you are logged into Overleaf or pushing a commit with your information to be able to track the contributors to the paper.

@@

\section{Introduction} \label{sec:intro}
% Moritz (first draft)

\section{Major concepts}
% Anyone want to take this??
\subsection{APEs - Astropy Proposals for Enhancement}
% would be nice to write about the concept of APEs so we can refer to the
% relevant ones latr in the text

@@

\section{Astropy Core Package v2.0}

The astropy project aims to provide python-based packages for all tasks that are commonly needed in a large subset of the astronomical community. Two aspects of this (time and coordinate transformations) are already discussed in great detail in section 3. In this section, we highlight other features introduced or substantially improved since version v0.2, which is described in \citet{2013A&A...558A..33A}.
(ordered in the order in which they appear in the astropy documentation)

@@

\section{Infrastructure for affiliated packages}
% - should we use links to the appropriate github repo?
%
\par In addition to astronomy related packages and libraries, the Astropy
Project also contains and supports several infrastructure package that are
very generic. The following sections describes the most widely used
selection of them.
%
\subsubsection{Package template}
% Brigitta may write this up if there is no other takers
\par Astropy provides a template package that any Python package is welcome to
use (many affiliated packages do so). The template contains a ready-to-go
package layout. It provides infrastructure such as documentation tools,
testing framework and CI templates and configurations, Cython integration,
and documentation on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
\texttt{ci-helpers} is a collection of scripts that empowers package
maintainers to control their testing set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the astropy ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for TravisCI and AppveyorCI.
%
\subsection{sphinx extensions}
% Tom R

@@

\section{Learning Astropy}
% Kelle, Adrian

@@

\section{The future of the Astropy project}

>>>>

\begin{itemize}
   \item The goal is to produce a brief and informative paper that covers major astropy principles not mentioned in the first paper, the core v2.0 package, and infrastructure in astropy project to support development in python.
	\item We don't plan on including code in this paper, but if you think you will need to include code in your section, please add it to a separate Python module (.py file) and include it in this repository.
    \item Use \escapecmd{\sectionname} not ``Section,'' \escapecmd{\figurename} not ``Figure''
    % I have never seen the \sectionname command and google is not any cleverer
    % Also, compilation fails when I use that. What's it good for?
    \item If your subpackage was included in Paper I, then please just include a note on what the package does, a reference to paper I, and any new major updates to your package
    \item If your subpackage was not included, then please a further description of the sub-package on level with what was in the first paper, and highlight any major features in it.   Typically length should be equivalent to one column
    \item Please make sure you are logged into Overleaf or pushing a commit with your information to be able to track the contributors to the paper.

@@

\section{Introduction} \label{sec:intro}
% first draft by Moritz (hamogu)
All astronomical research makes use of software in some way and
astronomy as a field has long supported the development of specialized
software tools for different astronomical tasks. Some of those
software packages are (or at least were) supported by large
institutions, e.g.\ IRAF \citep[developed at NAOA,][]{IRAF}, MIDAS
\citep[developed at ESO,][]{MIDAS}, or ds9 \citep[developed at
  SAO,][]{ds9}. These packages tend to address a wide range of users
and they typically provide some level of documentation and user
support. Other packages are developed foremost by individual research
groups and used mostly in work by members of this group. Those
packages can address more specialized needs, but are not necessarily
available to the community and even if they are, documentation can in
some cases be insufficient for new users and the quality of the
software, i.e. the robustness and the level of testing that has been
performed to ensure correctness, is not always clear. On the other
hand, there are also many widely used, well documented, high quality
software packages which are developed by individuals or small groups.

The implementation of astronomical software, be it for a package meant
for wide distribution or scripts and programs for a specific research
project, can be eased by the use of a library that provides core
functionality that is common to many astronomical tasks. Reading and
writing fits files is one example where it is time
consuming to implement the fits standard correctly and
programming is much faster when using an existing library perform this
task. Another example of such a common task is dealing with different
astronomical coordinate systems. The astropy project aims to provide a
library of core astronomical functionality in the Python programming
language.

Python\footnote{\url{https://www.python.org/}} is an increasingly
popular general-purpose scripting language that is available under a
permissive open source software licence free of charge for all major
operating systems. Stable and well-developed packages provide support
for array arithmetic \citep[numpy,][]{numpy}, a wide variety of
functions for scientific computing \citep[scipy,][]{numpy}, and
publication-quality plotting \citep[matplotlib,][]{matplotlib}. Tens of
thousands of other packages are available which can help with tasks
that are not astronomy specific but might be performed in the course
of astronomical research, e.g.\ presenting results on websites or
interfacing with databases.

At the same time, an ecosystem of tools, programms, and webservices
has become available that makes it easier to collaborate on code development,
continuously test the code, build and provide documentation, and
supply downloadable packages. The astropy project aims to develop and
provide high quality code and documentation according to the best
practices in software development. The project makes use of these
tools to do so without central institutional oversight.

The first public release of the astropy package is described in
\cite{2013A&A...558A..33A}. Since then, the astropy package has been
used in hundreds of projects, and the scope of the package as grown
considerably. At the same time, the community of astronomers
contributing to the project has grown tremendeously and an ecosystem
of packages supporting or affiliated with the astropy core has
developed. In this paper, we describe the current status of the
astropy community, the astropy core package, and the astropy
ecosystem.

We start by describing the way the astropy project works and is
organized in section~\ref{sec:concepts}.  The project develops a core
package called \texttt{astropy} (section~\ref{sec:core}) and several
separate packages that help setting up the infrastructure for testing,
documentation etc.\ (section~\ref{sec:infrastructure}). In
section~\ref{sec:learning} we give an overview of the wealth of
recources created to teach new users the use of the astropy packages
and how to contribute to the community. We end with a short vision for
the future of astropy in section~\ref{sec:future}.

\section{Major concepts}
\label{sec:concepts}
% Anyone want to take this??
\subsection{APEs - Astropy Proposals for Enhancement}
% would be nice to write about the concept of APEs so we can refer to the
% relevant ones latr in the text

@@

\section{Astropy Core Package v2.0}
\label{sec:core}
The astropy project aims to provide python-based packages for all tasks that are commonly needed in a large subset of the astronomical community. Two aspects of this (time and coordinate transformations) are already discussed in great detail in section 3. In this section, we highlight other features introduced or substantially improved since version v0.2, which is described in \citet{2013A&A...558A..33A}.
(ordered in the order in which they appear in the astropy documentation)

@@

\section{Infrastructure for affiliated packages}
\label{sec:infrastructure}
% - should we use links to the appropriate github repo?
%
\par In addition to astronomy related packages and libraries, the Astropy
Project also contains and supports several infrastructure package that are
very generic. The following sections describes the most widely used
selection of them.
%
\subsubsection{Package template}
% Brigitta may write this up if there is no other takers
\par Astropy provides a template package that any Python package is welcome to
use (many affiliated packages do so). The template contains a ready-to-go
package layout. It provides infrastructure such as documentation tools,
testing framework and CI templates and configurations, Cython integration,
and documentation on how to make it all work.
%
\subsection{Continuous integration helpers}
% Brigitta
\texttt{ci-helpers} is a collection of scripts that empowers package
maintainers to control their testing set up and installation process for
various continuous integration services via a set of environment
variables. While the current development is mostly driven by the needs of
the astropy ecosystem, the actual usage of this package is extremely
widespread. Currently we support setups for TravisCI and AppveyorCI.
%
\subsection{sphinx extensions}
% Tom R

@@

\section{Learning Astropy}
\label{sec:learning}
% Kelle, Adrian

@@

\section{The future of the Astropy project}
\label{sec:future}
